Comparative Analysis of the wav2vec 2.0 Feature Extractor

### 2023-02-27 main.tex
add todos/questions at end
update related work section, add w2v fe details

\section{Related work}
\draft{
Works on raw waveform acoustic modeling.

@@

Think about how to properly reference \cite{vieting2021waveform} without disclosing author information.
}

@@

>>>>

\section{Related work}
\draft{
Works on raw waveform acoustic modeling.
Think about how to properly reference \cite{vieting2021waveform} without disclosing author information.

@@

\cite{facebook2019wav2vec} uses 5 layers with kernel sizes (10, 8, 4, 4, 4) and strides which are always exactly half the kernel size.
All have 512 channels, a group normalization layer with a single group and a \relu nonlinearity.
\cite{facebook2020wav2vec2} uses seven layers with kernel sizes (10, 3, 3, 3, 3, 2, 2), strides (5, 2, 2, 2, 2, 2, 2), and a GELU activation function.
The first layer applies group normalization and finally, layer normalization and a linear projection is added.
}

@@

\section{To Dos/Questions}
\begin{itemize}
  \item \wvtwo feature extractor vs. feature encoder
\end{itemize}
